Results

### 2024-09-15 scripts/Results.Rmd
removed scouting points within 1km of known occurrences

# here are the ranked patches
f_rp <- list.files('../results/rankedPatches', pattern = '.shp')
f_rp <- data.frame(
  f_rankedp = paste0('../results/rankedPatches/', f_rp), 
  species = gsub('[.]shp$', '', f_rp)
)

@@

  wide <- dplyr::mutate(
    x, 
    suitability = suitability, 
    .before = geometry) |>
    dplyr::select(-f_suitability, -f_rankedp, -f_patchMetrics, -f_classMetrics) |>
    dplyr::left_join(lsm, by = c('PchIDComb' = 'id' ))

@@

@@

@@

suitability_amounts <- readRDS('../data/processed/prcntSDMsurfaceSuitable.rds')
suitability_amounts <- bind_rows(suitability_amounts)

>>>>

# here are the ranked patches
f_rp <- list.files('../results/rankedPatches-manuscript', pattern = '.shp')
f_rp <- data.frame(
  f_rankedp = paste0('../results/rankedPatches-manuscript/', f_rp), 
  species = gsub('[.]shp$', '', f_rp)
)

@@

  wide <- dplyr::mutate(
    x, 
    suitability = suitability, 
    .before = geometry) |>
    dplyr::select(-f_rankedp, -f_patchMetrics, -f_classMetrics) |>
    dplyr::left_join(lsm, by = c('PchIDComb' = 'id' ))

@@

 # for manuscript 193 records are NA.
```

Some of these visits undoubtedly arose due to revisits of known occurrences. 
We will discard any point within 500m of an historic point which we know was distributed to the crews via QGIS. 
```{r}
p <- '../data/raw/occurrence/combined_records'
f <- file.path(p, list.files(p, pattern = '.shp$'))

f_occ <- data.frame(
  f_rankedp = f, 
  taxa = gsub('[.]shp$', '', basename(f))
)

files <- left_join(scouting, f_occ, by = 'taxa') 
f <- split(files, f = files$f_rankedp)

strip_occurrences <- function(x){

  occurrences <- sf::st_read(sf::st_drop_geometry(x$f_rankedp[1]), quiet = T) |>
    sf::st_buffer(1000)

  ints <- sf::st_intersects(occurrences, x) # identify intersecting points
  removals <- unique(unlist(ints[lengths(ints) > 0])) # remove them.

  if(length(removals > 0)){
    x <- x[-removals,]
  }

  return(dplyr::select(x, -f_rankedp))
}

files <- lapply(f, strip_occurrences) |>
  bind_rows()

rm(f, p, strip_occurrences)
```

@@

scout_split <- split(files, files$taxa)
# we are going to discard species with fewer than 3 observations. 
scout_split <- scout_split[lapply(scout_split, nrow) >= 3]

@@

suitability_amounts <- readRDS('../data/processed/prcntSDMsurfaceSuitable.rds') |>
  bind_rows(suitability_amounts)
